A Motion Capture and Imitation Learning-based Approach to Robot Control

### 2022-06-20 tex-arxiv/article.tex
start writing prelim

\title{A Motion Capture and Imitation Learning-Based Approach to Robot Control}

@@

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{\textit{arXiv} Template}

@@

To help guide the development process and serve as a means of evaluation, a sample use case was selected -- object throwing. While on the surface the task is almost entirely defined by elementary ballistics that can be programmed explicitly, it serves as a convenient benchmark for robot programming by way of demonstrations. The task was deemed sufficiently non-trivial when considered from the perspective of a Markov Decision Process or time-series model only given limited information about system state at any given time step, while also being suitable for intuitive evaluation by human observers due to its intuitively straightforward nature. Furthermore, the relationship between release position, velocity and target coordinates provides an obvious way to quantitatively evaluate model performance against training and validation data -- extrapolated throw accuracy.

@@

>>>>

\title{A Motion Capture and Imitation Learning-based Approach to Robot Control}

@@

% Uncomment to override  the `A preprint' in the header
%\renewcommand{\headeright}{Technical Report}
%\renewcommand{\undertitle}{Technical Report}
\renewcommand{\shorttitle}{Motion Capture and Imitation Learning-based Robot Control}

@@

To help guide the development process and serve as a means of evaluation, a sample use case was selected -- object throwing. While on the surface the task is almost entirely defined by elementary ballistics that can be programmed explicitly, it serves as a convenient benchmark for robot programming by way of demonstrations. The task was deemed sufficiently non-trivial when considered from the perspective of a Markov decision process or time-series model only given limited information about system state at any given time step, while also being suitable for intuitive evaluation by human observers due to its intuitively straightforward nature. Furthermore, the relationship between release position, velocity and target coordinates provides an obvious way to quantitatively evaluate model performance against training and validation data -- extrapolated throw accuracy.

@@

In this article, an \emph{agent} can be taken to mean the part of the system that acts based on state or observation information $s$ in an \emph{environment}, according to a \emph{policy} $\pi$ which is specified by a parametric \emph{model} -- a function $\pi_{\theta}(s)$ with parameters $\theta$ tuned in optimization and produces an output \emph{action} $a$. In practice this means that references to the agent, model and policy are almost interchangeable in most contexts. A formalism common in both reinforcement and imitation learning contexts is the \emph{Markov decision process} (MDP), formally given by \citep{attia2018global}

\begin{equation}
	MDP = (S,A,T,R,I)
\end{equation}
where $S$ is the set of states $s$, $A$ is the (formally discrete) set of actions $a$, $T:S \times A \rightarrow S$ is a state transition function that encapsulates the environment, $R:S \rightarrow \mathbb{R}$ is a reward function associated with each state and $I = p\left(s_0 \in S\right)$ represents the initial state distribution. In many imitation learning related cases a reward function need not specified or considered, and, if one is willing to break with the strict formal definition and give up the use of mathematical tools defined only on finite probability distributions, continuous action spaces can also be considered.

One important characteristic of the MDP is that
